Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-11-13 manuscript.Rmd
Update results

# format the data
source('./scripts/primary-analyses/01_formatting_data.R')
source('./scripts/secondary-analyses/icews/01_formatting_data.R')
source('./scripts/secondary-analyses/phoenix/01_formatting_data.R')

@@

num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")

@@

The corpus of tweets used included `r sum(num_tweets$n)` Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter streaming API,
servers at the University of Texas at Austin collected the tweets. The servers
were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
directly to the high-bandwidth UT network maintained by IT services.

@@

# read in social cohesion data
cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")

# plot time series
raw_cohesion_ts <- ggplot(cohesion_df, aes(x= as.Date(Date), y=MeanCohesion)) +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")
ggsave("./results/primary/raw-cohesion-ts.png")

@@

A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for DET, NRLINE, maxL, and LAM. All other
metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
\autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of positive events
found no statistically significant difference from chance for any of the metrics
other than TT (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistically significant difference from chance for DET, NRLINE, L,
ENTR, LAM, and TT. All other metrics did not reach significance (Figure
\@ref(fig:plot-rp-targ); \autoref{table-1}).

@@

A qualitative investigation of the recurrence plots suggests a shift in dynamics
around the 36th observation, which corresponds to May 4th, 2012.

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for maxL, ENTR, and LAM (Figure
\@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistical difference from chance for DET, NRLINE, and rENTR. All other
metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

@@

Looking qualitatively at the recurrence plots, there again appeared to be a
shift in dynamics around the 36th observation (May 4th, 2012).

@@

For social cohesion and count of all events, there was a consistent period of
above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
one-week peaks at the beginning of the time period, DET was largely above chance
from the 46th to the 61st window, with some exceptions (Figure
\@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 50th window, with some exceptions during window
periods 19--30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 43rd--47th windows. DET was above or nearly
above chance in the 1st and 2nd windows, with intermittent peaks in later
windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
also showed above- or nearly above-chance values in windows 7--17 and
intermittent peaks between the 34th and 61st windows (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of positive events, there was a downward trend in
RR as the window moved, with largely above-chance values in the first 20 windows
and the 32nd--45th windows. DET stayed largely within chance, with the exception
of windows 13--19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and negative events, there was an extended, overlapping
period of time during which RR (32nd--47th windows) and DET (35th--39th windows)
were above or nearly above chance (Figure
\@ref(fig:plot-wcrqa-source-targ-all)). These windows span from May 3rd--14th,
2012.

>>>>

# format the data
source('./scripts/primary-analyses/01_formatting_data.R')

@@

#num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")

@@

The corpus of tweets used included r sum(num_tweets$n) (ADD TICKS) Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter streaming API,
servers at the University of Texas at Austin collected the tweets. The servers
were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
directly to the high-bandwidth UT network maintained by IT services.

@@

# read in social cohesion data
cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")

# plot time series
raw_cohesion_ts <- ggplot(cohesion_df, aes(x= as.Date(Date), y=MeanCohesion)) +
  geom_point() +
  geom_line() +
  #geom_errorbar(aes(ymin=len-ci, ymax=len+ci), colour="black", width=.1, position=pd) +
  xlab("Date") +
  ylab("Mean Social Cohesion")
ggsave("./results/primary/raw-cohesion-ts.png")

@@

A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for DET, NRLINE, and LAM. All other
metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
\autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for DET, NRLINE, maxL, LAM, and TT. All other
metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistically significant difference from chance for maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).

@@

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found
a statistical difference from chance for maxL and LAM. All other metrics
were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive events
found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and LAM (Figure
\@ref(fig:plot-rp-source-targ); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistical difference from chance for rENTR. All other
metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
\autoref{table-2}).

@@

@@

For social cohesion and count of all events, there was a consistent period of
above-chance RR from the 2nd--12th and 44th--50th window. DET was largely above chance
from the 47th to the 52nd window, with some exceptions (Figure
\@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 18th window, with an exception for window 17. A peak also appeared for the 40th--42nd windows. DET was intermitently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 46th--49th windows and was below chance for extneded period from the 56th--62nd window. DET bottomed out at zero for the 15th--23rd and 34th--39th windows. The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 2nd--18th and 44th--52nd windows. DET
also showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of positive events, there was a downward trend in
RR as the window moved, with above-chance values in the first 23 windows
and the 57th--62nd windows. DET stayed largely within chance, with the exception
of windows 1 and 4 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and negative events, RR was aboce chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows. DET showed a upward trend as the windows moved. It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows. (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).
